### 2024-03-05 src/paper.tex
Minor fix
Remove equation number
Fix start states in postive closure

\Ex
\begin{equation}
  \RE{r}_1 = \Kleene{(\Char{b} \Seq (\Char{a} \Seq \Char{b})?)} \Seq \Char{c} \\
\end{equation}
\begin{align*}
  \Automaton{r_1} &= (\Set{Q}_1, \Alphabet, \delta_1, q_{0, 1}, \Set{F}_1)\\[1em]
  \Set{Q}_1 &= \{1, 2, 3\} \\[1em]
  \Alphabet &= \{\Char{a}, \Char{b}, \Char{c}\} \\[1em]
  \delta_1(1, \Char{b}) & =  2\\
  \delta_1(2, \Char{a}) & =  1\\
  \delta_1(2, \Char{b}) & =  2\\
  \delta_1(2, \Char{b}) & =  3\\[1em]
  q_{0, 1} &= 1 \\[1em]
  \Set{F}_1 &= \{3\}
\end{align*}

\begin{center}
\begin{tabular}{ | c | c | c | c | }
   \hline
   $\delta_1$ & \Char{a} & \Char{b} & \Char{c} \\
   \hline
  1 & $\Err$ & 2 & $\Err$  \\
   \hline
  2 & 1 & 2 & 3  \\
   \hline
  3 & $\Err$ & $\Err$ & $\Err$   \\
   \hline
\end{tabular}
\end{center}

@@

@@

\begin{gather*}
  \RE{r}_2 = \Kleene{(\Char{b} \Seq (\Char{a} \Spc \Char{b})?)} \Seq \Char{c} \\
  \Automaton{\RE{r}_2} = (\Set{Q}_2, \Alphabet, \delta_2, q_{0, 2}, \Set{F}_2)
\end{gather*}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
    }
    \node[state, initial, label=above left:$\Automaton{\RE{r}}$] (u0) {$\Pos\Char{a}$};
    \node[state, right=of u0] (u1) {$\Char{a}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
  \end{tikzpicture}
\end{center}

@@

\begin{tcolorbox}[title={Definicija}]
  \begin{equation*}
    \begin{aligned}
      \KleenePlus{\RE{s}} &= \RE{s} \Union \RE{s} \Seq \RE{s} \Union \RE{s} \Seq \RE{s} \Seq \RE{s} \Union \ldots \\
      &= \Rep{\RE{s}}{1} \Union \Rep{\RE{s}}{2} \Union \ldots \\
      &= \Big\vert_{i = 1}^\infty \Rep{\RE{s}}{i}\\
      \Language{\KleenePlus{\RE{s}}} &= \bigcup_{i = 1}^\infty \Language{\RE{s}^i}\\[1em]
      \Kleene{\RE{s}} &= \Null \Union \KleenePlus{\RE{s}} = \Opt{(\KleenePlus{\RE{s}})} = \KleenePlus{(\Opt{\RE{s}})}\\
      \Language{\Kleene{\RE{r}}} &= \{\Str{}\} \cup \Language{\KleenePlus{\RE{r}}}
    \end{aligned}
  \end{equation*}
\end{tcolorbox}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
    }
    \node[state, initial, accepting, label=above left:$\Automaton{\RE{r}}$] (u0) {$\KleenePlus{(\Pos\Char{a})}$};
    \node[state, accepting, right=of u0, label={above right:=}] (u1) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \node[state, accepting, right=of u1, label={above right:=}] (u2) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
    \draw (u1) edge[->] node[auto]{$\Char{a}$} (u2);

    \node[state, initial, below=of u0, accepting, label=above left:$\Automaton{\RE{r}}$] (p0) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \node[state, accepting, right=of p0] (p1) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \draw (p0) edge[->] node[auto]{$\Char{a}$} (p1);
    \draw (p1) edge[->, loop right] node[auto]{$\Char{a}$} (p1);
  \end{tikzpicture}
\end{center}

>>>>

\Ex
\begin{equation*}
  \RE{r}_1 = \KleenePlus{(\Char{b} \Seq (\Char{a} \Seq \Char{b})?)} \Seq \Char{c} \\
\end{equation*}
\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.append style={minimum size=0.5cm},
      initial text=$ $
    }

@@

\begin{align*}
  \Automaton{r_1} &= (\Set{Q}_1, \Alphabet, \delta_1, q_{0, 1}, \Set{F}_1)\\[1em]
  \Set{Q}_1 &= \{1, 2, 3\} \\[1em]
  \Alphabet &= \{\Char{a}, \Char{b}, \Char{c}\} \\[1em]
  \delta_1(1, \Char{b}) & =  2\\
  \delta_1(2, \Char{a}) & =  1\\
  \delta_1(2, \Char{b}) & =  2\\
  \delta_1(2, \Char{b}) & =  3\\[1em]
  q_{0, 1} &= 1 \\[1em]
  \Set{F}_1 &= \{3\}
\end{align*}

\begin{center}
\begin{tabular}{ | c | c | c | c | }
   \hline
   $\delta_1$ & \Char{a} & \Char{b} & \Char{c} \\
   \hline
  1 & $\Err$ & 2 & $\Err$  \\
   \hline
  2 & 1 & 2 & 3  \\
   \hline
  3 & $\Err$ & $\Err$ & $\Err$   \\
   \hline
\end{tabular}
\end{center}
\Ex

@@

\begin{gather*}
  \RE{r}_2 = \KleenePlus{(\Char{b} \Seq (\Char{a} \Seq \Char{b})?)} \Seq \Char{c} \\
  \Automaton{\RE{r}_2} = (\Set{Q}_2, \Alphabet, \delta_2, q_{0, 2}, \Set{F}_2)
\end{gather*}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
    }
    \node[state, initial, label=above left:$\Automaton{\RE{r}}$] (u0) {$\Pos\Char{a}$};
    \node[state, accepting, right=of u0] (u1) {$\Char{a}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
  \end{tikzpicture}
\end{center}

@@

\begin{tcolorbox}[title={Definicija}]
  \begin{equation*}
    \begin{aligned}
      \KleenePlus{\RE{s}} &= \RE{s} \Union \RE{s} \Seq \RE{s} \Union \RE{s} \Seq \RE{s} \Seq \RE{s} \Union \ldots \\
      &= \Rep{\RE{s}}{1} \Union \Rep{\RE{s}}{2} \Union \ldots \\
      &= \Big\vert_{i = 1}^\infty \Rep{\RE{s}}{i}\\
      \Language{\KleenePlus{\RE{s}}} &= \bigcup_{i = 1}^\infty \Language{\RE{s}^i}
    \end{aligned}
  \end{equation*}
\end{tcolorbox}

\begin{tcolorbox}[title={Pravila}]
  \begin{equation*}
    \begin{aligned}
      \Kleene{\RE{s}} &= \Null \Union \KleenePlus{\RE{s}} = \Opt{(\KleenePlus{\RE{s}})} = \KleenePlus{(\Opt{\RE{s}})}\\
      \Language{\Kleene{\RE{r}}} &= \{\Str{}\} \cup \Language{\KleenePlus{\RE{r}}}
    \end{aligned}
  \end{equation*}
\end{tcolorbox}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
    }
    \node[state, initial, label=above left:$\Automaton{\RE{r}}$] (u0) {$\KleenePlus{(\Pos\Char{a})}$};
    \node[state, accepting, right=of u0, label={above right:=}] (u1) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \node[state, accepting, right=of u1, label={above right:=}] (u2) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
    \draw (u1) edge[->] node[auto]{$\Char{a}$} (u2);

    \node[state, initial, below=of u0, label=above left:$\Automaton{\RE{r}}$] (p0) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \node[state, accepting, right=of p0] (p1) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \draw (p0) edge[->] node[auto]{$\Char{a}$} (p1);
    \draw (p1) edge[->, loop right] node[auto]{$\Char{a}$} (p1);
  \end{tikzpicture}
\end{center}
